Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-02-21 paper/paper.tex
pass on eval

\usepackage{libertine}
\usepackage{lipsum}% http://ctan.org/pkg/lipsum
\usepackage{algorithm}% http://ctan.org/pkg/algorithm
\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx
\usepackage{graphicx}
\usepackage[compatibility=false]{caption}% http://ctan.org/pkg/caption
\usepackage{booktabs}
%% \usepackage{cite}
\usepackage{url}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{tikz}
\usetikzlibrary{matrix,fit,shapes,calc,positioning,shadows,arrows,shapes,backgrounds,decorations.markings,fadings}
\usepackage{listings}
\usepackage[caption=false, font=footnotesize]{subfig}
\renewcommand{\ttdefault}{pcr}
\lstset{
  basicstyle=\scriptsize\ttfamily,
  keywordstyle=\scriptsize\ttfamily\bfseries,
  language=C,             % choose the language of the code
  frame=single,              % adds a frame around the code
  aboveskip=0pt,
  belowskip=0pt,
  breaklines=true,           % sets automatic line breaking
  breakatwhitespace=false,   % sets if automatic breaks should only happen at
  showspaces=false,
  %numbersep=5pt,              % Abstand der Nummern zum Text
  %tabsize=2,                  % Groesse von Tabs
  %extendedchars=true,         %
  %breaklines=true,            % Zeilen werden Umgebrochen
  keywords=[2]{tcp, flag, threshold, track, count, seconds, classtype, sid}
}
\usepackage{balance}
\usepackage{wrapfig}
\usepackage{enumitem}
\usepackage{color, colortbl}
\definecolor{Gray}{gray}{0.9}

@@

\begin{figure}[H]
  \centering
  \scalebox{1.2}{
    \begin{tikzpicture}
      \begin{axis}[
          bar width=6pt,
          scaled ticks=false,
          tick label style={/pgf/number format/fixed},
          ybar stacked,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          symbolic x coords={0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10},
          xtick=data,
          nodes near coords,
          every node near coord/.append style={font=\tiny},
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(0,11) (1,1301) (2,4910) (3,3662) (4,3250) (5,5353) (6,2911) (7, 1337) (8, 1246) (9,763) (10, 495)};
      \end{axis}
    \end{tikzpicture}
  }
  \vspace{-2ex}
  \caption{\label{fig:distribution-rule-size}Distribution of rule sizes.}
\end{figure}

@@

\begin{figure}[t!]
  \centering
  \scalebox{1.2}{  
    \begin{tikzpicture}
      \begin{axis}[
          bar width=6pt,
          scaled ticks=false,
          tick label style={/pgf/number format/fixed},
          ybar stacked,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          symbolic x coords={0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10},
          xtick=data,
          nodes near coords,
          every node near coord/.append style={font=\tiny},
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(0,2134) (1,9164) (2,5103) (3,5841) (4,1987) (5,1622) (6,805) (7, 535) (8, 340) (9,154) (10, 53)};
      \end{axis}
    \end{tikzpicture}
  }
  \caption{\label{fig:distribution-contents}Distribution of number of
    content options.}
\end{figure}

@@

\begin{figure}[t!]
  \centering
  \scalebox{1.2}{  
    \begin{tikzpicture}
      \begin{axis}[
          bar width=6pt,
          scaled ticks=false,
          tick label style={/pgf/number format/fixed},
          ybar stacked,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          symbolic x coords={GET, POST, SELECT, UNION, id=, DELETE, UPDATE, INSERT, 200, /index.php?},
          xtick=data,
          xticklabel style={rotate=45},          
          nodes near coords,
          every node near coord/.append style={font=\tiny},
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(GET,2007) (POST,1570) (SELECT,747) (UNION,461) (id=,408) (DELETE,390) (UPDATE,387) (INSERT, 386) (200, 352) (/index.php?, 273)};
      \end{axis}
    \end{tikzpicture}
  }
  \caption{\label{fig:distribution-strings}Distribution of strings
    used as parameters of content options.}
\end{figure}

@@

\begin{figure}[t!]
  \centering
  \scalebox{1.2}{
    \begin{tikzpicture}
      \begin{axis}[
          ybar stacked,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          %          ylabel={\#rules},
          symbolic x coords={http\_method, http\_uri, http\_user\_agent, http\_header, http\_host, http\_connection, http\_request\_line},
          xtick=data,
          xticklabel style={rotate=45},          
          nodes near coords,
          every node near coord/.append style={font=\scriptsize},        
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(http\_method,3821) (http\_uri,10111) (http\_user\_agent,1022) (http\_header,4089) (http\_host,224) (http\_connection,29) (http\_request\_line,11)};
      \end{axis}
    \end{tikzpicture}
  }
  \vspace{-2ex}
  \caption{\label{fig:distribution-content_modifiers}Content modifiers
    frequency.}
\end{figure}

@@

@@

@@

\begin{table*}[h!]
  \small
  \caption{\label{table:attacks}List of attacks.}
  \centering
  \begin{tabular}{lllp{11cm}}
    \toprule
    \multicolumn{1}{c}{Name} &
    \multicolumn{1}{c}{Category} &
    \multicolumn{1}{c}{Protocol} &
    \multicolumn{1}{c}{Groud Truth} \\
    \midrule     
    Ping Scan & Active Recon. & ICMP & \textbf{dsize}:0; \textbf{itype}:8; \\
    SYN Flood & DoS & TCP & \textbf{flags}: S,12; \textbf{threshold}: type both, track by\_dst, count 5000, seconds 5;\\

@@

\subsection{Objects of Analysis}
\label{sec:dataset-benign}

@@

@@

\subsubsection{Attack reproduction.}\label{attack-reproduction} \tname{} requires the attack to
be replayed in order to check whether or not the rule it generates
captures the attack.  See function $\mathit{isPlausible}$, used in the
minimization algorithm from Section~\ref{sec:minimization}. For all
attacks listed on Table~\ref{table:attacks}, we found scripts
available on the web to replay the attacks. For example, the SYN Flood
attack can be replayed with hping3~\cite{hping3}, using the following
command: \CodeIn{hping3 -d 80 -w 64 -S -p 80 --flood --rand-source
  <IP>}. With the script to reproduce the attack, we executed the
following steps to obtain ``pcap'' files, which abstracts network
messages~\cite{pcap}, to run \tname:~1)~instantiate the script (\eg{},
define the IP, for the example above), 2)~execute the script,
3)~monitor the traffic with the wireshark network
monitor~\cite{wireshark-net-monitor}.

@@

\subsection{Results}

>>>>

\usepackage{subcaption}
\usepackage{libertine}
\usepackage{lipsum}% http://ctan.org/pkg/lipsum
\usepackage{algorithm}% http://ctan.org/pkg/algorithm
\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx
\usepackage{graphicx}
\usepackage[compatibility=false]{caption}% http://ctan.org/pkg/caption
\usepackage{booktabs}
%% \usepackage{cite}
\usepackage{url}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{tikz}
\usetikzlibrary{matrix,fit,shapes,calc,positioning,shadows,arrows,shapes,backgrounds,decorations.markings,fadings}
\usepackage{listings}
%\usepackage[caption=false, font=footnotesize]{subfig}
\renewcommand{\ttdefault}{pcr}
\lstset{
  basicstyle=\scriptsize\ttfamily,
  keywordstyle=\scriptsize\ttfamily\bfseries,
  language=C,             % choose the language of the code
  frame=single,              % adds a frame around the code
  aboveskip=0pt,
  belowskip=0pt,
  breaklines=true,           % sets automatic line breaking
  breakatwhitespace=false,   % sets if automatic breaks should only happen at
  showspaces=false,
  %numbersep=5pt,              % Abstand der Nummern zum Text
  %tabsize=2,                  % Groesse von Tabs
  %extendedchars=true,         %
  %breaklines=true,            % Zeilen werden Umgebrochen
  keywords=[2]{tcp, flag, threshold, track, count, seconds, classtype, sid}
}
\usepackage{balance}
\usepackage{wrapfig}
\usepackage{enumitem}
\usepackage{color, colortbl}
\definecolor{Gray}{gray}{0.9}

@@

@@

\begin{figure*}[t!]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \scalebox{1.2}{  
    \begin{tikzpicture}
      \begin{axis}[
          bar width=6pt,
          scaled ticks=false,
          tick label style={/pgf/number format/fixed},
          ybar stacked,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          symbolic x coords={0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10},
          xtick=data,
          nodes near coords,
          every node near coord/.append style={font=\tiny},
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(0,2134) (1,9164) (2,5103) (3,5841) (4,1987) (5,1622) (6,805) (7, 535) (8, 340) (9,154) (10, 53)};
      \end{axis}
    \end{tikzpicture}
  }
  \vspace{-1ex}
  \caption{\label{fig:distribution-contents}Number of content options.}
\end{subfigure}% <---- don't forget this %
%\vspace{1ex}
%\\
\begin{subfigure}{.5\textwidth}
  \centering
  \scalebox{1.2}{
    \begin{tikzpicture}
      \begin{axis}[
          bar width=6pt,
          scaled ticks=false,
          tick label style={/pgf/number format/fixed},
          ybar stacked,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          symbolic x coords={0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10},
          xtick=data,
          nodes near coords,
          every node near coord/.append style={font=\tiny},
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(0,11) (1,1301) (2,4910) (3,3662) (4,3250) (5,5353) (6,2911) (7, 1337) (8, 1246) (9,763) (10, 495)};
      \end{axis}
    \end{tikzpicture}
  }
  \vspace{-1ex}
  \caption{\label{fig:distribution-rule-size}Rule sizes.}
\end{subfigure}%
%\vspace{1ex}
\\
\begin{subfigure}{.5\textwidth}
  \centering
  \scalebox{1.2}{  
    \begin{tikzpicture}
      \begin{axis}[
          bar width=6pt,
          scaled ticks=false,
          tick label style={/pgf/number format/fixed},
          ybar stacked,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          symbolic x coords={GET, POST, SELECT, UNION, id=, DELETE, UPDATE, INSERT, 200, /index.php?},
          xtick=data,
          xticklabel style={rotate=45},          
          nodes near coords,
          every node near coord/.append style={font=\tiny},
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(GET,2007) (POST,1570) (SELECT,747) (UNION,461) (id=,408) (DELETE,390) (UPDATE,387) (INSERT, 386) (200, 352) (/index.php?, 273)};
      \end{axis}
    \end{tikzpicture}
  }
  \vspace{-3ex}  
  \caption{\label{fig:distribution-strings}Strings used as parameters of content options.}
\end{subfigure}%
%\vspace{1ex}
%\\
\begin{subfigure}{.5\textwidth}
  \centering
  \scalebox{1.2}{
    \begin{tikzpicture}
      \begin{axis}[
          ybar stacked,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          %          ylabel={\#rules},
          symbolic x coords={http\_method, http\_uri, http\_user\_agent, http\_header, http\_host, http\_connection, http\_request\_line},
          xtick=data,
          xticklabel style={rotate=45},          
          nodes near coords,
          every node near coord/.append style={font=\scriptsize},        
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(http\_method,3821) (http\_uri,10111) (http\_user\_agent,1022) (http\_header,4089) (http\_host,224) (http\_connection,29) (http\_request\_line,11)};
      \end{axis}
    \end{tikzpicture}
  }
  \vspace{-1ex}
  \caption{\label{fig:distribution-content_modifiers}Content modifiers
    frequency.}
\end{subfigure}%
\vspace{-1ex}
  \caption{Distribution of features.}
\end{figure*}

@@

@@

@@

\begin{table*}[t!]
  \small
  \caption{\label{table:attacks}List of attacks.}
  \centering
  \begin{tabular}{lllp{11cm}}
    \toprule
    \multicolumn{1}{c}{Name} &
    \multicolumn{1}{c}{Category} &
    \multicolumn{1}{c}{Protocol} &
    \multicolumn{1}{c}{Groud Truth} \\
    \midrule     
    Ping Scan & Active Recon. & ICMP & \textbf{dsize}:0; \textbf{itype}:8; \\
    SYN Flood & DoS & TCP & \textbf{flags}: S,12; \textbf{threshold}: type both, track by\_dst, count 5000, seconds 5;\\

@@

\newcommand{\textRQone}{How well \tname\ ranks the golden rule?}
\vspace{0.2cm}
\begin{itemize}[leftmargin=*]
\item{\textbf{RQ1.}} \textRQone
\end{itemize}

\textbf{Rationale.}~The golden rule is a rule that is known to capture
a given attack. \tname\ generates several rules that satisfy the
invariant to only capture the malicious traffic, but the amount of
data we use to assess that invariant, albeit large, is limited. In
fact, assessing quality of each rule (\ie{}, fitness to the attack)
requires domain knowledge. The position of the golden rule at the
ranking produced by \tname\ is a proxy measure to the effort of a
system administrator in finding the rule that fits the purpose.

\newcommand{\textRQtwo}{What is the importance of heuristic functions in ranking?}
\vspace{0.2cm}
\begin{itemize}[leftmargin=*]
\item{\textbf{RQ2.}} \textRQtwo\
\end{itemize}

@@

@@

\subsection{Objects of Analysis}
\label{sec:dataset-benign}
\label{attack-reproduction}

@@

  \tname{} requires the attack to
be replayed in order to check whether or not the rule it generates
captures the attack.  See function $\mathit{isPlausible}$, used in the
minimization algorithm from Section~\ref{sec:minimization}. For all
attacks listed on Table~\ref{table:attacks}, we found scripts
available on the web to replay the attacks. For example, the SYN Flood
attack can be replayed with hping3~\cite{hping3}, using the following
command: \CodeIn{hping3 -d 80 -w 64 -S -p 80 --flood --rand-source
  <IP>}. With the script to reproduce the attack, we executed the
following steps to obtain ``pcap'' files, which abstracts network
messages~\cite{pcap}, to run \tname:~1)~instantiate the script (\eg{},
define the IP, for the example above), 2)~execute the script,
3)~monitor the traffic with the wireshark network
monitor~\cite{wireshark-net-monitor}.

@@

@@

\subsection{Answering RQ1: \textRQone}

\subsection{Answering RQ2: \textRQtwo}
